### 2014-07-03 tex/pseudo-code.tex
Added

\section{Pseudo-code}
\figref{fig:surface-syntax} defines the surface syntax for the
Javalite language \cite{saints-MS}. \figref{fig:machine-syntax} is
the machine syntax. Javalite is syntactic machine
defined as rewrites on a string. The semantics use a CEKS model with a (C)ontrol string representing the expression being
evaluated, an (E)nvironment for local variables, a (K)ontinuation for
what is to be executed next, and a (S)tore for the heap.

>>>>

\section{Generalized Symbolic Execution with Lazy Initialization}
Generalized symbolic execution with lazy initialization is a technique
to apply symbolic execution to non-primitive data types (i.e.,
objects) \cite{GSE03}. The approach initializes each symbolic object
to be either null, a new instance of the object, or an alias to an
object previously created as part of lazy initialization. Each of
these outcomes is a possible choice, and a model checker is able to
exhaustively enumerates these choices effectively creating all
possible concrete heaps under the choice sets. The approach is first formalized in this section and then extended to describe the precise heap summaries.

Many of these concrete
heaps explore redundant control flow paths in the program under test,
but since symbolic model checking is stateless, subject to a bound to
terminate the search, the model checker needlessly explores many
redundant state leading to severe state explosion.

\figref{fig:surface-syntax} defines the surface syntax for the
Javalite language \cite{saints-MS}. \figref{fig:machine-syntax} is
the machine syntax. Javalite is syntactic machine
defined as rewrites on a string. The semantics use a CEKS model with a (C)ontrol string representing the expression being
evaluated, an (E)nvironment for local variables, a (K)ontinuation for
what is to be executed next, and a (S)tore for the heap.
